NEW Italy and Upenn samples

### 2020-12-12 scripts/40_combine_all_samp_pheno.Rmd
aaaaahh i need to give a lab meeting presentation again on Dec 21
update
good Im making progess and continue sorting things out

@@

@@

all_baseline <- bind_rows(I, M, P)
```

>>>>

I2 <- read_csv('../data/shotgun_pheno/italy_all_later.csv') %>% 
  select(fid)

@@

P2 <- read_csv('../data/shotgun_pheno/upenn_all_later.csv') %>% 
  select(fid)

@@

all_baseline <- bind_rows(I,I2, M, P, P2)

all_baseline %>% 
  write_csv('../data/shotgun_input/samples_cart_all_msk_patial_italy_upenn.csv', col_names = F)
```

## the pheno label for the samples

```{r}
I1 <- read_csv('../data/shotgun_pheno/italy_all_earlier.csv') %>% 
  filter(timepoint < 0) %>% 
  ungroup() %>% 
  select(fid, cr_d30:toxicity)

# the pheno lable for the I2!
iptb <- readxl::read_excel('/Volumes/castoricenter/CAR-Tcell_and_Microbiota/Italy/patients/italy_essential_data_v4.xlsx', sheet = 1)
I2_pheno <- I2 %>% 
  rename(pt_id = pid) %>% 
  left_join(iptb) %>% 
  select(fid, cr_d30:toxicity)

I_phe <- bind_rows(
  I1, I2_pheno
) %>% 
  mutate(center = 'I')

# upenn
P_ptb <- readxl::read_excel('/Volumes/castoricenter/CAR-Tcell_and_Microbiota/U Penn/patients/upenn_essential_data_v3.xlsx', sheet = 1)

P_ptb_ineligible <- readxl::read_excel('/Volumes/castoricenter/CAR-Tcell_and_Microbiota/U Penn/patients/upenn_essential_data_v3.xlsx', sheet = 2)

P_ <- bind_rows(
  P %>% 
    mutate(pt_id = str_replace(fid, 'MS_UPENN_','')) %>% select(fid, pt_id) %>% mutate(pt_id = as.numeric(pt_id)),
  P2 %>% 
    mutate(pt_id = as.numeric(fid)) %>% select(fid, pt_id)
) %>% 
  filter(! pt_id %in% P_ptb_ineligible$pt_id)

P_phe <- P_ %>% 
  left_join(P_ptb)  %>% 
  select(fid, cr_d30:toxicity) %>% 
  select(fid, cr_d30, cr_d100, cr_overall, toxicity)  %>% 
  mutate(center = 'P')

# MSK
M_phe <- M %>% 
  select(fid, cr_d30:toxicity) %>% 
  mutate(center = 'M')

# combined

all <- bind_rows(
  M_phe, P_phe, I_phe
)

# a tally table
all %>% 
  count(center, toxicity)

all %>% 
  count(center, cr_d30)
```

### 2020-12-12 scripts/41_new_I_E_shotgun.Rmd
good Im making progess and continue sorting things out

fntb_I <- shotgun_lookup_ad %>% 
  filter(projectid == 'Project_11453' & str_detect(fid, "^CMT")) %>% 
  # first see if that patient is eligible or not 
  mutate(pid = str_extract(fid, 'CMT...')) %>% 
  filter(! pid %in% ineligible$pt_id)  %>% 
  filter(!str_detect(fid, '_$')) %>% # the dups
  separate(fid, into = c('pre','day'), remove = F, convert = T, sep = '_') %>% 
  filter(is.na(day)) %>% # remove the ones I'm sure to be after infusion
  filter(fid != 'CMT029G0') %>%  # CMT029G0 is actually day 1 sample
  select(-pre, -day)
```
```{r}
fntb_P <- shotgun_lookup_ad %>%
  filter(projectid == 'Project_11453' & !str_detect(fid, "^CMT"))
```

>>>>

fntb_I <- shotgun_lookup_ad %>% 
  filter(projectid == 'Project_11453' & str_detect(fid, "^CMT")) %>% 
  # first see if that patient is eligible or not 
  mutate(pid = str_extract(fid, 'CMT...')) %>% 
  filter(! pid %in% ineligible$pt_id)  %>% 
  filter(!str_detect(fid, '_$')) %>% # the dups
  separate(fid, into = c('pre','day'), remove = F, convert = T, sep = '_') %>% 
  filter(is.na(day)) %>% # remove the ones I'm sure to be after infusion
  filter(fid != 'CMT029G0') %>%  # CMT029G0 is actually day 1 sample
  select(-pre, -day)
```

```{r}
fntb_I %>% 
  write_csv('../data/shotgun_pheno/italy_all_later.csv')
```

## Upenn ones

```{r}
fntb_P <- shotgun_lookup_ad %>%
  filter(projectid == 'Project_11453' & !str_detect(fid, "^CMT"))
```

```{r}
fntb_P %>% 
  write_csv('../data/shotgun_pheno/upenn_all_later.csv')
```
